%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{Böse}%
%
\whitecard{Böse}{Kleiderbügel- Abtreibung.}%
\whitecard{Böse}{AIDS.}%
\whitecard{Böse}{Alle Kekse vor einem AIDS-Spendenlauf essen.}%
\whitecard{Böse}{Auschwitz.}%
\whitecard{Böse}{Auto- kannibalismus.}%
\whitecard{Böse}{Ein Fötus.}%
\whitecard{Böse}{Nekrophilie.}%
\whitecard{Böse}{Eine Pyramide aus abgetrennten Köpfen.}%
\whitecard{Böse}{Ein Tiefkühlschrank voller Organe.}%
\whitecard{Böse}{Ein starker Mongoloid.}%
\whitecard{Böse}{Erträgliche Transvestiten.}% original: passable
\whitecard{Böse}{Frauen an einer Abtreibungsklinik anmachen.}%
\whitecard{Böse}{Hungersnot.}%
\whitecard{Böse}{Jüdische Burschenschaften.}%
\whitecard{Böse}{Kinder mit Arsch-Krebs.}%
\whitecard{Böse}{Kindes- missbrauch.}%
\whitecard{Böse}{Kinnhaken.}%
\whitecard{Böse}{Kreuzigung.}%
\whitecard{Böse}{Männerfleisch.}%
\whitecard{Böse}{Menschenfleisch.}%
\whitecard{Böse}{Amputierte.}% before: Menschen mit Amputationen
\whitecard{Böse}{Mit Pockenviren versehene Decken.}%
\whitecard{Böse}{Rassenhygiene.}%
\whitecard{Böse}{Robo-Hitler.}% original: Mecha-Hitler
\whitecard{Böse}{Schlecht getimte Holocaust-Witze.}%
\whitecard{Böse}{Schwer- behinderte.}%
\whitecard{Böse}{Teile eines toten Anhalters.}%
\whitecard{Böse}{Tote Babies.}%
\whitecard{Böse}{Tote Eltern.}%
\whitecard{Böse}{Weiße mit Afros.}%
\whitecard{Böse}{Zwergenwerfen.}%
\whitecard{Böse}{Massenmord mit einem Fahrzeug.}% before: vehikulärer -> is not a German word - original: Körperverletzung mit einem Fahrzeug
\whitecard{Böse}{Pedophile.}%
\whitecard{Böse}{Afrikanische Kinder.}%
\whitecard{Böse}{Eine Windmühle voller Leichen.}%
\whitecard{Böse}{Einen Scheiß um die Dritte Welt scheren.}%
\whitecard{Böse}{Skalps von weißen Männern.}%
\whitecard{Böse}{Privilegien der Weißen.}%
\whitecard{Böse}{Zivile Opfer.}% before: Verlust von Zivilisten
\whitecard{Böse}{Lepra.}%
\whitecard{Böse}{Seppuku.}%
\whitecard{Böse}{Ethnische Säuberung.}%
\whitecard{Böse}{Kriegsbedingte Amputationen.}%
\whitecard{Böse}{Die jährliche Massenhinrichtung.}%
%
\blackcard{1}{Böse}{Wofür ist Krieg gut?}%
\blackcard{1}{Böse}{Das Leben der Indianer wurde für immer verändert, als die Weißen Männer ihnen \underl zeigten.}%
\blackcard{1}{Böse}{Was haben die USA den Kindern in Afganistan vom Flugzeug abgeworden?}%
\blackcard{1}{Böse}{Menschen, die aussehen wie \underl.}%
