%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{Kultur}%
\whitecard{Kultur}{Arnold Schwarzenegger.}%
\whitecard{Kultur}{Cards against Humanity.}%

\whitecard{Kultur}{Darth Vader.}%
\whitecard{Kultur}{Das\newline Cookie Monster.}%
\whitecard{Kultur}{Die Macht.}%

\whitecard{Kultur}{Eine M. Night\newline Shyamalan\newline Story-Wendung.}%
\whitecard{Kultur}{Ein Live-Studio Publikum.}%
\whitecard{Kultur}{Ein\newline Amateurvideo\newline von Heidi Klum,\newline wie sie in eine\newline Dose Ravioli\newline heult.}%

\whitecard{Kultur}{Justin Bieber.}%
\whitecard{Kultur}{Keanu Reeves.}%
\whitecard{Kultur}{Lady Gaga.}%

\whitecard{Kultur}{Michael Jackson.}%
\whitecard{Kultur}{Michael \newline``Bully''\newline Herbig.}%
\whitecard{Kultur}{Miley Cyrus mit 55.}%

\whitecard{Kultur}{Nickelback.}%
\whitecard{Kultur}{Nicolas Cage.}%
\whitecard{Kultur}{Oompa-Loompas.}%

\whitecard{Kultur}{Robert Downey, Jr.}%
\whitecard{Kultur}{RoboCop.}%
\whitecard{Kultur}{Sean Connery.}%

\whitecard{Kultur}{Sido.}%
\whitecard{Kultur}{Star Trek.}%
\whitecard{Kultur}{Thomas the Train.}%

\whitecard{Kultur}{Vera Int-Veen}%
\whitecard{Kultur}{William Shatner.}%
\whitecard{Kultur}{Winnie der Puh.}%

\whitecard{Kultur}{Til Schweiger.}%
\blackcard{1}{Kultur}{In Ihrem neuen Film hat Hannah Montana zum ersten Mal mit \underl zu kämpfen.}%
\blackcard{1}{Kultur}{Bevor ich Sie töte, Herr Bond, muss ich Ihnen \underl zeigen.}%

\blackcard{1}{Kultur}{Bald zu sehen: \underl, das Musical.}%
\blackcard{2}{Kultur}{Das neue Superhelden/Kumpan Duo! Es ist \underl und \underl.}%
\blackcard{1}{Kultur}{Demnächst erscheint: Harry Potter und die Kammer der \underl.}%

\blackcard{1}{Kultur}{Gleich auf RTL:\newline die Weltmeisterschaft der \underl.}%
\blackcard{1}{Kultur}{RTLs neue Reality-TV-Show - Jetzt mit 8 Stars die mit \underl zusammenleben.}%
\blackcard{1}{Kultur}{Was hat Vin Diesel zum Mittag gegessen?}%

\blackcard{1}{Kultur}{Was ist Batmans geheime Vorliebe?}%
\blackcard{2}{Kultur}{Dreamworks präsentiert: "\underl,\newline die Geschichte von \underl."}%
\blackcard{1}{Kultur}{In M. Night Shyamalans neuen Film findet Bruce Willis heraus, dass \underl in Wirklichkeit die ganze Zeit \underl war.}%

\blackcard{1}{Kultur}{99 \underl auf ihrem Weg zum Horizont.}%
