%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{Eklig}%
%
\whitecard{Eklig}{Brennende Scheiße.}%
\whitecard{Eklig}{Ein Ball aus Ohrenschmalz, Sperma und Fußnägeln.}%
\whitecard{Eklig}{Ein bisschen einnässen.}% before: pinkeln
\whitecard{Eklig}{Ein heimlicher Arschkratzer.}%
\whitecard{Eklig}{Einnässen.}%
\whitecard{Eklig}{Durchfall. Für immer.}%
\whitecard{Eklig}{Ein Kind festhalten und es anfurzen.}%
\whitecard{Eklig}{Furzen und einfach weggehen.}% before: dann weglaufen
\whitecard{Eklig}{Fressen und Kotzen.}%
\whitecard{Eklig}{``Poop Back and Forth. Forever!``}% reference: "Me and You and Everyone We Know" -> translation?
\whitecard{Eklig}{Sich einkacken.}% original: einscheißen
\whitecard{Eklig}{Sich überfressen und dann abführen.}%
\whitecard{Eklig}{Smegma.}%
\whitecard{Eklig}{Tod durch Durchfall.}%
\whitecard{Eklig}{Unterwäsche wenden, um sie nicht waschen zu müssen.}% original: falsch herum tragen
\whitecard{Eklig}{Würgen ohne Erbrechen.}%
\whitecard{Eklig}{Ein endloser Strom aus Diarrhoe.}%
\whitecard{Eklig}{Zwei Zwerge, die in einen Eimer scheißen.}% before: Kleinwüchsige
\whitecard{Eklig}{An Dünnschiss sterben.}%
\whitecard{Eklig}{Thomas Gottschalks weicher, verschrumpelter Körper.}%
\whitecard{Eklig}{Vollgeschissene Windeln.}%
\whitecard{Eklig}{Wenn man furzt und ein bisschen Kacke mit rauskommt.}%
\whitecard{Eklig}{Einen Rülpser erwarten und stattdessen auf den Boden kotzen.}%
\whitecard{Eklig}{Fotzenfürze.}% original: Vaginalfürze
%
\blackcard{2}{Eklig}{Für meinen nächsten Trick werde ich \underl aus \underl rausziehen.}%
\blackcard{1}{Eklig}{Was lässt mich unkontrolliert furzen?}%
