%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{FSK 16}%
%
\whitecard{FSK 16}{50.000 Volt genau in die Nippel.}%
\whitecard{FSK 16}{Daniel Radcliffes appetitliches Arschloch.}%
\whitecard{FSK 16}{Der weibliche Orgasmus.}%
\whitecard{FSK 16}{Eine Anmache.}%
\whitecard{FSK 16}{Eine freche schwarze Frau.}% before: erotische
\whitecard{FSK 16}{Ein gebleichtes Arschloch.}%
\whitecard{FSK 16}{Ein kaputtes Kondom.}%
\whitecard{FSK 16}{Ein Mikropenis.}%
\whitecard{FSK 16}{Ein natürliches Aphrodisiakum.}%
\whitecard{FSK 16}{Erektile Dysfunktion.}%
\whitecard{FSK 16}{Feuchte Träume.}% original: feuchter Traum
\whitecard{FSK 16}{Fliegende Sex-Schlangen.}%
\whitecard{FSK 16}{Heavy Petting.}% original: Third Base (https://en.wikipedia.org/wiki/Baseball_metaphors_for_sex)
\whitecard{FSK 16}{Erotische Kissen- schlachten.}% original: sexy
\whitecard{FSK 16}{Genitalpircings.}%
\whitecard{FSK 16}{Geschmackvolle Seitentitte.}% original: sideboob, before: Dekolleté
\whitecard{FSK 16}{Harald Schmidts Hoden im Vorhang verfangen.}%
\whitecard{FSK 16}{Hodentorsion.}%
\whitecard{FSK 16}{Hose mit ausgespartem Hintern.}%
\whitecard{FSK 16}{``Ihn'' rausholen.}% original: Es rausholen.
\whitecard{FSK 16}{Klitoris.}%
\whitecard{FSK 16}{Lance Armstrongs fehlender Hoden.}%
\whitecard{FSK 16}{Masturbation.}%
\whitecard{FSK 16}{Meine Vagina.}%
\whitecard{FSK 16}{Nippelpiercings.}%
\whitecard{FSK 16}{Oma nackt sehen.}%
\whitecard{FSK 16}{Penis-Atem.}%
\whitecard{FSK 16}{Penis-Finger.}%
\whitecard{FSK 16}{Sanftes Liebkosen der Oberschenkel- innenseite.}%
\whitecard{FSK 16}{Halbherziges Vorspiel.}%
\whitecard{FSK 16}{So sauer werden, dass man einen Ständer bekommt.}%
\whitecard{FSK 16}{Stephen Hawking, der versaut redet.}% before: Sexgespräche
\whitecard{FSK 16}{Ein Mann am Rande des Orgasmus.}%
\whitecard{FSK 16}{Testikuläre Verdrehung.}%
\whitecard{FSK 16}{Überraschungs- sex!}%
\whitecard{FSK 16}{Völlig nackt.}%
\whitecard{FSK 16}{Vorhäute.}% original: Vorhaut
\whitecard{FSK 16}{Erotische Harry-Potter Geschichten.}% before: Literatur
\whitecard{FSK 16}{Laktation.}%
\whitecard{FSK 16}{Sexuelle Spannungen.}%
\whitecard{FSK 16}{Sich nackt ausziehen und KiKa gucken.}% original: Nickelodeon
\whitecard{FSK 16}{Einvernehm-\newline licher Sex.}%
\whitecard{FSK 16}{Alice Schwarzers Vagina.}%
\whitecard{FSK 16}{Bilder von Brüsten.}% original: Titten
\whitecard{FSK 16}{Eine Erektion, die länger als vier Stunden dauert.}%
\whitecard{FSK 16}{Einen Ständer verstecken.}% before: Erektion
\whitecard{FSK 16}{Eregierte Nippel.}%
\whitecard{FSK 16}{Freunde mit gewissen Vorzügen.}%
\whitecard{FSK 16}{Holzfäller Phantasien.}%
\whitecard{FSK 16}{Mein Sexleben.}%
\whitecard{FSK 16}{Schenkel- schnorcheln.}%
\whitecard{FSK 16}{Panda Sex.}%
\whitecard{FSK 16}{Eine Schnappschildkröte, die einem in die Penisspitze beißt.}%
%
\blackcard{1}{FSK 16}{Eine Studie ergab, dass Teenager 50 Prozent weniger Sex hatten, nachdem man ihnen \underl zeigte.}%
\blackcard{1}{FSK 16}{Ich denke während dem Sex gerne über \underl nach.}%
\blackcard{2}{FSK 16}{Sie sagten, wir wären verrückt. Sie sagten, wir könnten nicht \underl in \underl stecken. Sie lagen falsch.}%
\blackcard{1}{FSK 16}{Wie verlor ich meine Jungfräulichkeit?}%
