%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{Geschichte}%
%
\whitecard{Geschichte}{Adolf Hitler.}%
\whitecard{Geschichte}{Anders Breivik.}%
\whitecard{Geschichte}{Der Amoklauf von Winnenden.}%
\whitecard{Geschichte}{Historische schwarze Kollegen.}%
\whitecard{Geschichte}{Der Versailler Vertrag.}%
\whitecard{Geschichte}{Genghis Khan.}%
\whitecard{Geschichte}{Hurrikan Katrina.}%
\whitecard{Geschichte}{Kim Jong-il.}%
\whitecard{Geschichte}{Lee Harvey Oswald.}%
\whitecard{Geschichte}{Sklaverei.}%
\whitecard{Geschichte}{Unser erster Chimpansen-Kanzler.}%
\whitecard{Geschichte}{Wikinger.}%
\whitecard{Geschichte}{Ein Zeitreise-Paradoxon.}%
\whitecard{Geschichte}{Der Urknall.}%
\whitecard{Geschichte}{Katapulte.}%
\whitecard{Geschichte}{Marcus Iunius Brutus.}%
\whitecard{Geschichte}{Beidseitige Bereitschaft zum nuklearen Gegenschlag.}%
\whitecard{Geschichte}{Der Übermensch.}%
\whitecard{Geschichte}{In Polen einmarschieren.}%
\whitecard{Geschichte}{Gandhi.}%
\whitecard{Geschichte}{Martin Luther King.}%
%
\blackcard{1}{Geschichte}{Mit dem Ziel, mehr Besucher anzulocken, eröffnet das Naturkundemuseum eine interaktive Ausstellung über \underl.}% before: Das Naturkundemuseum stellt jetzt auch \underl aus. - original: Beim Versuch...das Smithsonian Museum of Natural History...
\blackcard{1}{Geschichte}{``Ich weiß nicht, mit welchen Waffen der 3. Weltkrieg gekämpft wird, aber der 4. Weltkrieg wird mit \underl gekämpft.``}% ref. to Albert Einstein
\blackcard{1}{Geschichte}{Was ist in 1000 Jahren unsere Währung, wenn Papiergeld nur eine entfernte Erinnerung ist?}%
