%
% This file is part of Cards Against Humanity Fullformat German.
%
% Cards Against Humanity Fullformat German is free software:
% you can redistribute it and/or modify it under the terms of the
% GNU General Public License as published by the Free Software Foundation,
% either version 3 of the License, or (at your option) any later version.
%
% Cards Against Humanity Fullformat German is distributed in the hope that it
% will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Cards Against Humanity Fullformat German.
% If not, see <http://www.gnu.org/licenses/>.
%
%
% Please note: All whitespace characters might break this document. Please
% avoid placing whitespace character that are not intended inside these files.
%
\titlecard{Werbung}%
%
\whitecard{Werbung}{5 Euro Subway Footlongs.}%
\whitecard{Werbung}{Activia\SymbReg.}%
\whitecard{Werbung}{Astra.}%
\whitecard{Werbung}{Auf Rolex umsteigen.}%
\whitecard{Werbung}{Bifi\SymbReg.}%
\whitecard{Werbung}{Das Michelin-Männchen.}%
\whitecard{Werbung}{Der Ahoi-Brause Mann.}%
\whitecard{Werbung}{Der kalte, erfrischende Geschmack einer Pepsi\SymbReg}%
\whitecard{Werbung}{Eine Super Soaker\SymbReg  voller Katzenpisse.}% before: Schwamm
\whitecard{Werbung}{Euphoria\SymbReg  von Calvin Klein.}%
\whitecard{Werbung}{AXE\SymbReg  Deo.}%
\whitecard{Werbung}{Dibadibadu.}%
\whitecard{Werbung}{Happy Hippos.}% 
\whitecard{Werbung}{McDonalds Einmaleins.}%
\whitecard{Werbung}{Meister Proper Sauberkraft.}%
\whitecard{Werbung}{Meister Proper, direkt hinter dir.}%
\whitecard{Werbung}{Ronald McDonald.}%
\whitecard{Werbung}{Dominos\SymbReg  Oreo\SymbReg  Dessert Pizza.}%
\whitecard{Werbung}{World of Warcraft.}%
\whitecard{Werbung}{Viagra\SymbReg.}%
\whitecard{Werbung}{Ein Bop It\SymbReg!}%
\whitecard{Werbung}{Die Make-A-Wish\SymbReg  Stiftung.}%
\whitecard{Werbung}{Whiskas.}% original: Fancy Feast
\whitecard{Werbung}{All-you-can-eat Shrimps für 4,99 Euro.}%
\whitecard{Werbung}{Das schwedische Tempur-Pedic\SymbReg\newline Schlafsystem.}%
%
\blackcard{1}{Werbung}{Ein romantisches Essen bei Kerzenschein wäre unvollständig ohne \underl.}%
\blackcard{1}{Werbung}{Statt der Rute bring der Weihnachtsmann unartigen Kindern jetzt \underl.}% original: Kohle ... bösen Kindern...
\blackcard{1}{Werbung}{\underl: Von Kindern getestet, von Müttern empfohlen.}% original: mit Kindern getestet, von Müttern freigegeben
\blackcard{1}{Werbung}{\underl: Gut bis zum letzten Tropfen.}%
\blackcard{1}{Werbung}{Was ist das nächste Happy Meal\SymbReg  Spielzeug?}%
\blackcard{1}{Werbung}{\underl macht Kinder froh und Erwachsene ebenso.}%
\blackcard{1}{Werbung}{\underl, davon kann man nicht nur einen haben!}%
